\documentclass{book}

\begin{document}
    So if you have ever met an engineer, you would know that we love to stick our noses in everything.
    This may have something to do with our propensity for being right all the time, but that's extraneous.
    The real problem is that we just care so damn much.
    I'm pretty sure that most people think that we're trying to prove how smart we are, or that we think everyone else is stupid.
    However, the real fact of the matter is that sometimes a solution to someone else's problem just presents itself.
    What's really amazing is how little some people want to make their lives easier.
    That's basically how I'm expecting the reception of this book to go.
    People will say ``Stupid Civil engineer, what do you know about the design of cities?''
    I'll preface this by saying I don't have any formal training in urban design, I just design buildings for a living.
    What I can say, is that I pay attention and that I do my research.
    Based on that, is that lots of cities almost seem like they've been designed to make people unhappy.
    You've probably been waiting for me to say this, but I think that nature is responsible.

    Now before you string me up for heresy and throw me off of the nearest green roof, I don't think that trees and clean air are responsible for our plight.
    The real problem lies in where our cities are built, and how nature sometimes facilitates their slow creep  across the landscape.
    Our natural inclination is to fill all of the space available to us.
    After all, why go through the trouble of building a massive mixed use building with commercial property and apartments for a couple dozen people when you can spend the same amount and build another suburb on the outskirts of town.
    This just means that people get further and further away from their jobs, spending longer and longer on their commutes and becoming more and more dependent on cars.
    This also becomes a problem for the city.
    Maintenance on new roads quickly becomes unmanageable, and any attempts to implement public transit systems are basically doomed from the start.
    Basically, the natural landscape is facilitating our destruction of the environment. 
\end{document}
